A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-10 paper.tex
Remove figures and tables

\section{System Design Thinking}
\label{section:design_thinking}
\subsection{Data subscription-based trading platform players}
There are three major roles, data providers, data consumers and brokers which are similar to the pub/sub messaging model. But unlike the standard pub/sub model where brokers link the publishers and subscribers who are not aware of each others, in our proposed architecture, the brokers are only responsible for message delivery and essential verification processes. As shown in Fig.~\ref{fig:pub_sub_model}.

\begin{figure}[!t]
    \centering
    \includegraphics[width=3.5in]{pub_sub_model}
    \caption{The players in data subscription-based trading platform consists of data providers, data consumers and brokers.}
    \label{fig:pub_sub_model}
\end{figure}

@@

Through TangleID, entities get a public/private key pair, the location of DID document and the seed (i.e., the identifier of its owner in IOTA) that generates the DID document MAM public channel. The public/private key pair can be used to exchange sensitive data and establish the trust communication, where messages that are encrypted with a public key can only be decrypted with private key owner. During data subscription process, the encryption keys of data products are encrypted with data consumers' public key on DID document which ensures only the subscribed consumers are accessible. See Fig.~\ref{fig:TangleID}

\begin{figure}[h]
    \centering
    \includegraphics[width=3.5in]{TangleID}
    \caption{To participate the data trading, players are required to have DID document issued by TangleID. The Consumer first need to send a registration request to TangleID to get the MAM channel ID of DID document and a public/private key pair for authentication. When the trade establish, the consumer sends the DID MAM channel ID to provider in order to perform encryption key exchange. The data provider can then retrieve the consumer's public key and encrypt the content with it. After the consumer gets the encrypted message, he/she can decrypt the ciphertext with private key and finally get the encryption key of data product.}
    \label{fig:TangleID}
\end{figure}

@@

\subsection{Delegate MAM operations to Tangle-accelerator}
\label{section:ta_endpoint}
MAM builds a secure and authenticated communication protocol on top of multiple cryptosystems, which low-level devices need to spend a lot of resources to apply it, and they may not even support built-in libraries in regular operating system. To overcome these concerns, we propose another approach that allows data providers to delegate the MAM operations to Tangle-accelerators, proxy servers with high computation power, which can accelerates the interactions with Tangle while ensuring the privacy of data providers. Fig.~ \ref{fig:ta_struct} shows the structure of Tangle-accelerator, and Fig.~\ref{fig:delegation} shows how data providers can adopt MAM.

\begin{figure}[!t]
    \centering
    \includegraphics[width=3.5in]{ta_structure}
    \caption{Tangle-accelerator distribute IOTA api requests to idle IOTA nodes (i.e., full nodes) and provide Proof-of-Work acceleration. It can also cache the requests/responses in a key-value store to shorten response time, and automatically resend requests if failed. Tangle-accelerators also form a firewall for full nodes, which don't need to reveal the IP address to public and reduce the risks of being attacks.}
    \label{fig:ta_struct}
\end{figure}

@@

Also, data provider will change the encryption key of data product to prevent unsubscribers access to rest of the data. The new key should be updated to the remaining subscribers in $consumer2Purchase$ list in Product Contract. Fig.~\ref{fig:unsubscribe} shows the unsubscription flow.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=3.5in]{unsubscribe}
    \caption{Once a data consumer launch a unsubscription procedure, he/she is added to unsubscriber list and the Product Contract will distribute the funds to provider, broker and consumers respectively. Then, the data provider will generate a new encryption key and upload it for every remaining subscribers.}
    \label{fig:unsubscribe}
\end{figure}

@@

\begin{table}[htbp]
	\caption{Time measurement of channel creation}
	\label{tab:channel_create}
	\begin{center}
	\begin{tabular}{|c|c|c|}
	\hline
		\textbf{height of MSS} & \textbf{PC (sec)} & \textbf{Raspberry Pi 3 (sec)} \\ 
		\hline
		1 & 0.26183 & 2.908702 \\ 
		2 & 0.524076 & 5.805524 \\ 
		3 & 1.045942 & 11.555660 \\ 
		4 & 2.092989 & 23.178036 \\ 
		5 & 4.19515 & 46.164079\\ 
		6 & 8.361586 & 92.320173\\ 
		7 & 16.651607 & 185.292243\\
		\hline
	\end{tabular}
	\end{center}
\end{table}

\begin{table}[htbp]
	\caption{Time measurement of endpoint creation}
	\label{tab:endpoint_create}
	\begin{center}
	\begin{tabular}{|c|c|c|}
	\hline
		\textbf{height of MSS} & \textbf{PC (sec)} & \textbf{Raspberry Pi 3 (sec)} \\ 
		\hline
		1 & 0.256425 & 2.887064 \\ 
		2 & 0.505679 & 5.767912 \\ 
		3 & 0.999524 & 11.550455 \\ 
		4 & 1.994017 & 23.260508 \\ 
		5 & 3.965007 & 46.748366 \\ 
		6 & 7.918925 & 93.182975 \\ 
		7 & 16.561419 & 186.064562 \\
		\hline
	\end{tabular}
	\end{center}
\end{table}

The results of Table \ref{tab:channel_create} and Table \ref{tab:endpoint_create} are plotted in Fig.~\ref{fig:mam_create}. Since the creation of channel and endpoint are MSS calculations, the curves of the same hardware are nearly identical. On the other hand, the performance of Raspberry Pi 3 is acceptable when \textit{height} is smaller than 4, but time grows rapidly when \textit{height} is 5 or above. And the performance of PC remains acceptable even \textit{height} gets to 7. The results indicate that MAM channel/endpoint creation is a laborious job for a Raspberry Pi 3 when data providers need a longer channel/endpoint, which is one of the reason that MAM operations should be forwarded to brokers.

>>>>

\section{System Design Thinking}
\label{section:design_thinking}
\subsection{Data subscription-based trading platform players}
There are three major roles, data providers, data consumers and brokers which are similar to the pub/sub messaging model. But unlike the standard pub/sub model where brokers link the publishers and subscribers who are not aware of each others, in our proposed architecture, the brokers are only responsible for message delivery and essential verification processes.

@@

Through TangleID, entities get a public/private key pair, the location of DID document and the seed (i.e., the identifier of its owner in IOTA) that generates the DID document MAM public channel. The public/private key pair can be used to exchange sensitive data and establish the trust communication, where messages that are encrypted with a public key can only be decrypted with private key owner. During data subscription process, the encryption keys of data products are encrypted with data consumers' public key on DID document which ensures only the subscribed consumers are accessible.

@@

\subsection{Delegate MAM operations to Tangle-accelerator}
\label{section:ta_endpoint}
MAM builds a secure and authenticated communication protocol on top of multiple cryptosystems, which low-level devices need to spend a lot of resources to apply it, and they may not even support built-in libraries in regular operating system. To overcome these concerns, we propose another approach that allows data providers to delegate the MAM operations to Tangle-accelerators, proxy servers with high computation power, which can accelerates the interactions with Tangle while ensuring the privacy of data providers. Fig.~\ref{fig:delegation} shows how data providers can adopt MAM.

@@

Also, data provider will change the encryption key of data product to prevent unsubscribers access to rest of the data. The new key should be updated to the remaining subscribers in $consumer2Purchase$ list in Product Contract.

@@

@@

Fig.~\ref{fig:mam_create} shows the results of channel/endpoint creation. Since the creation of channel and endpoint are MSS calculations, the curves of the same hardware are nearly identical. On the other hand, the performance of Raspberry Pi 3 is acceptable when \textit{height} is smaller than 4, but time grows rapidly when \textit{height} is 5 or above. And the performance of PC remains acceptable even \textit{height} gets to 7. The results indicate that MAM channel/endpoint creation is a laborious job for a Raspberry Pi 3 when data providers need a longer channel/endpoint, which is one of the reason that MAM operations should be forwarded to brokers.
